Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-04-26 Ben_Manuscripts/transport/Draft.tex
updated draft.

  In addition to geometric factors which make H\textsubscript{II} membranes
  ideal for selective separations, they have the potential to further disrupt
  conventional membrane separation techniques by being selective based not
  only on solute size and charge, but on chemical functionality as well. 
  The functional LLC monomer head groups that occupy the pore region of the
  membrane can interact with solutes. Dischinger et al.~studied the 
  performance of a Q\textsubscript{I} phase LLC membrane, which has a 
  similar pore topology to the H\textsubscript{II} phase, but a more 
  tortuous geometry, and observed a range of selectivities dependent on the
  anion coordinated to the LLC monomer.~\cite{dischinger_effect_2017} Intelligent 
  design of LLC monomers can help us tailor membranes for solute-specific
  separations.

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. The separation performance of these membranes has been 
  primarily characterized with size-exclusion experiments which emphasizes 
  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
  While size-exclusion is a useful separation, it cannot reliably purify a 
  solution where the solute size is on the same order as water. Therefore, it is
  important to take advantage of material properties other than pore size. 
  Unfortunately, interactions between solutes and pore moieties have yielded
  unclear trends in experimental transport studies.~\cite{dischinger_effect_2017}

  Molecular dynamics (MD) simulations can give us mechanistic insights with 
  atomistic resolution so that we can directly observe small solute transport
  within LLC membrane nanopores and intelligently design new membranes for 
  solute-specific separations. In our previous work, we used MD simulations to 
  determine the most likely structure of the hexagonal phase formed by the monomer
  Na-GA3C11, expanding upon the most recent experimental characterization.~\cite{coscia_understanding_2018,feng_thin_2016}
  We developed techniques for equilibrating the hexagonal phase formed by neat 
  monomer as well as with varying amounts of water in the pores.

  %BJC: is a figure with all the solutes necessary? would take up a lot of space. maybe supporting
  In this work, we have studied the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character. We have listed the solutes studied along with the abbreviations that
  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
  Note that, in order to avoid studying charge species, we have only studied
  %BJC: citations for pKa's
  acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
  pKa of acetic acid is 4.75. Assuming that the pKa of gallic acid is similar 
  to NaGA3C11, it is possible for our sodium salted monomer to exist at the 
  same time as protonated acetic acid.

%  % BJC: not sure if I should just leave formatting to the journal. Thought tcolorbox was neat though
%  % I can easily change these abbreviations and have them applied to all the figures. I haven't given
%  % them much thought. Just used their residue names
%  \begin{table}
%  \centering
%  \begin{tcolorbox}[%
%  	colframe=blue,
%  	title=\centering \textbf{Solute Names and Their Abbreviations},
%  	width=0.7\textwidth,
%  	box align=center,
%  	halign=center,
%  	valign=center,
%  	fontupper=\linespread{1}\selectfont]
%
%  \begin{multicols}{2}
%
%  \textbf{Name} \\
%  Acetic Acid \\
%  Acetamide \\
%  Acetone \\
%  Butanol \\
%  Dimethyl Formamide \\
%  2,3-Dimercapto-1-propanol \\
%  Dimethyl Sulfoxide \\
%  Ethyl Acetate \\ 
%  Ethanol \\
%  Ethylene Glycol \\
%  Glycerol \\
%  Methanol \\ 
%  Propylene Carbonate \\
%  Propylene Glycol \\
%  Propanol \\
%  Ribose \\
%  Mercaptoethanol \\
%  Tetrose \\
%  Tetrahydrofuran \\
%  Urea \\
%  \columnbreak
%
%  \textbf{Abbrevation} \\
%  AcOH \\  % Acetic acid
%  AcN \\  % Acetamide
%  ACE \\  % Acetone
%  BtOH \\  % Butanol
%  DMF \\  % Dimethyl Formamide
%  DMP \\  % 2,3-Dimercapto-1-propanol
%  DMSO \\  % Dimethyl sulfoxide
%  ETAC \\  % Ethyl Acetate
%  EtOH \\  % ethanol
%  EG \\  % ethylene glycol
%  GLY \\  % glycerol
%  MeOH \\  % methanol
%  PC \\ % propylene carbonate
%  PG \\  % propylene glycol
%  PrOH \\  % propanol
%  RIB \\ 
%  ME \\ % mercaptoethanol
%  TET \\
%  THF \\ 
%  URE \\
%  
%  \end{multicols}
%  
%  %MRS2: can you put molecules in the table as well? I think it would be better for reference. Some of the larger ones may have small molecules. You can potentially partially stagger them horizontally so the size can be OK? 
%  \end{tcolorbox}
%  \caption{}\label{table:abbreviations}
%  \end{table}

@@

  We first address the structure of the pores formed in the membrane.
  Previously, we have studied dry membrane systems and some systems with 
  low water content. We will observe how the radial density of monomer 
  components and water change within the pore based on membrane water content.

  We then present our efforts to understand how small molecules, 
  including water, partition within the pores. From a macroscopic perspective,
  it is straightforward to hypothesize that the water and polar solutes spend
  their time exclusively in the tube-like hydrophilic pore region. Our
  previous work showed that there is a gradual compositional transition from
  the hydrophilic to the hydrophobic region which means that solutes may not
  necessarily stay confined to the centers of the pores or even within the 
  pore region. We then study the gradient in composition of solutes and 
  water and any resultant influence it might have on mechanistic properties.

  For the remainder of the paper, we present our observations 
  and explanations of the observed transport mechanisms exhibited by water
  and solutes. Given that the pores will restrict motion of the solutes, we
  anticipate that transport will be hindered in some way.

@@

  There are also a couple of points that this study is not intended to address. 
  First, we will not study the concentration dependence of the observed transport
  rates. Although the average MSD might change with concentration, we are 
  focused on the underlying solute-membrane interactions that lead to the 
  observed transport mechanisms which we conjecture will be the same 
  regardless of concentration. Second, we will not study the chemical potential
  of solutes in the pores, which could give us a better understanding of 
  equilibrium solute partitioning. This information will not greatly enhance our
  understanding of mechanistic details in various membrane regions. Both of the
  above points will add unnecessary levels of complexity which can be left for
  a future study. This work is a simple starting point meant for observing
  the types of interactions which occur between isolated solutes and the
  membrane.

@@

  We observed that water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition. We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent. We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95\% of their time outside of the distal tail region.

@@

  To study a given solute, we added 6, equally spaced in $z$, solute molecules to the
  center of each pore of the equilibrated cross-linked configuration. Our choice of 6
  solutes per pore provided a balance of a useful amount of data for generating 
  statistics and a low degree of interaction between solutes (see 
  Section~\ref{S-section:solute_interaction} of the Supporting Information). At each
  insertion point we placed a randomly oriented solute molecule then ran a short 
  energy minimization. We allowed the solutes to equilibrate for 5 ns using berendsen
  pressure control then collected transport data over the course of 1 $\mu$s MD simulations.

  \subsection{Solute Parameterization}\label{method:parameterization}

  We parameterized the interaction potential for the monomer and solutes using 
  the Generalized AMBER Force Field (GAFF)~\cite{wang_development_2004} with the
  Antechamber package \cite{wang_automatic_2006} shipped with AmberTools16~\cite{case_ambertools16_2016}.
  We use GAFF since it has been parameterized for use with organic molecules. We
  assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
  with QUACPAC from Openeye Scientific Software.

@@

  We measured the time-averaged $z$-direction mean squared displacement (MSD) of the
  centers of mass (COM) of each solute over the course of 1 $\mu$s MD simulations using 
  Equation~\ref{eqn:tamsd}:
  \begin{equation}
	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
	\label{eqn:tamsd}
  \end{equation}
  where $\tau$ is the time lag and T is the length of the trajectory~\cite{meroz_toolbox_2015}. 
  Generally, the MSD grows according to Equation~\ref{eqn:msd_form}:
  \begin{equation} 
	\langle z^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_\alpha$ is the generalized diffusion 
  coefficient. A value of $\alpha < 1$ indicates a subdiffusive process, while a value 
  of $\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
  motion respectively.
    % MRS1: time vs. ensemble MSD better in follow-up paper.
    % BJC2: I think it makes sense to mention, otherwise it looks like we don't 
    % fully understand the theory since I talk about subdiffusion in terms of 
    % alpha which is always calculated based on ensemble MSD unless we know for sure that
    % the system is ergodic (which it isn't the case for CTRW)
  In practice, $\alpha$ corresponds to the growth of the \textit{ensemble} MSD given
  by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
  \begin{equation}
	\langle z^2(t) \rangle = \langle z(t) - z(0) \rangle
	\label{eqn:ensemble_msd}
  \end{equation}
  Since the ensemble MSD is calculated with respect to a reference position, it carries
  some dependence on its starting point. The time-averaged MSD averages over all possible
  time lags of a given length, effectively eliminating any initial configuration 
  dependence and generating	an increased number of observations. For ergodic systems, 
  both types of MSDs will be equal. Since we have a small number of solutes with which to
  generate statistics and because we are not calculating values of $\alpha$ for this 
  particular study,	we will only use the time-averaged MSD.

@@

  The $z$-direction MSD of water in the 10 wt\% system is linear. Therefore, for
  the purpose of comparison, we calculated its diffusion constant by fitting a line
  to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
  is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
  by 2 (rather than 6) because we only measured the diffusion coefficient in one 
  dimension.

@@

  The Stokes-Einstein relationship expresses the diffusion coefficient of 
  a hard spherical particle as a function that is inversely related to the
  particle's radius:
  \begin{equation}
  D = \dfrac{k_bT}{6\pi\eta fr}
  \label{eqn:stokes-einstein}
  \end{equation}
  where $k_b$ and $T$ are the Boltzmann	constant and the system temperature
  respectively and $\eta$ is the system's viscosity. Here we have also 
  included the microfriction correction factor, $f$, introduced by 
  Gierer and Wirtz~\cite{gierer_molekulare_1953,chen_diffusion_1984} for when
  solute size becomes on the order of solvent size since the solute can no 
  longer be treated as a non-interacting hard sphere. $f$ is defined in terms
  of the ratio of $r_1$ and $r_2$, the radii of the solute and solvent molecules
  respectively:
  \begin{equation}
  f = \left(1.5\dfrac{r_2}{r_1} + \dfrac{1}{1 + \dfrac{r_2}{r_1}}\right)^{-1}
  %f = \left(1.5(r_2/r_1) + \dfrac{1}{1 + (r_2/r_1)}\right)^{-1}
  \label{eqn:correction_factor}
  \end{equation}
  For consistency with the presentation of our results, rather than calculate trends
  in $D$, we will apply Equation~\ref{eqn:stokes-einstein} in order to analyze 
  trends in solute MSDs, which is only valid because all trajectories are of the 
  same length.
%  However, this assumes linear behavior
%  of the MSD, which we will show is not that case. Our main usage of the 
%  Stokes-Einstein relationship is to show that solutes in our system do not 
%  behave as it predicts.
  % Possible comps question: Stokes law restricted to Re < 0.1, but we have no flow so Re ~ 0.

@@

  In order to measure the length of hops, we first needed to detect
  when they occurred. We used an off-line change point detection 
  algorithm, implemented in the python package \texttt{ruptures}
  \cite{truong_ruptures:_2018}, in order to determine at which 
  points hops occurred in the time series of each solutes' COM. We
  used the 3 dimensional COM positions of each solute, rather than
  just the $z$-direction, in order to detect lateral hops. However,
  hop lengths are reported as their displacement the $z$-direction.
  We reported the standard error in the average hop lengths by 
  bootstrapping the hop lengths.
  % BJC: could add more detail about which algorithm and cost function
  % penalty I used. Seems unnecessary since it is all in my code.

  We determined the frequency of hops by dividing the total number of 
  hops by the total length of the simulation. We used the average
  frequency as the $\lambda$ parameter in a Poisson distribution. We
  calculated the 95\% confidence intervals of the distribution based
  on its cumulative distribution function.

@@

  Based on the geometric criteria proposed by Luzar and Chandler 
  \cite{luzar_effect_1996}, we determined a hydrogen bond to exist if the
  distance between the donor, D, and acceptor, A, atoms is less than 
  3.5 \AA~and the angle formed by D--H$\cdot\cdot\cdot$A is less than 30\degree. Attempts
  to describe a hydrogen bond in the context of molecular simulations has
  yielded a number of definitions with no true consensus 
  \cite{prada-gracia_quest_2013} especially since the geometry of hydrogen
  bonds has some dependence on the system being studied. The definition of
  Luzar and Chandler is easily visualized for trajectories using the 
  \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
  package which allows us to directly check the validity of identified hydrogen bonds.
  In Section~\ref{S-section:hbond_sensitivity} of the Supporting Information, we
  show that our conclusions are insensitive to this definition within a 
  reasonable range.

  We determined the average percentage of solutes which actively participated
  in a hydrogen bond interaction with monomers each frame. We only counted
  unique solute--monomer hydrogen bond interactions meaning solutes
  that hydrogen bond more than once simultaneously were classified as a
  single pairing event. We determined the standard error of this calculation
  by bootstrapping over each solute's trajectory. For each bootstrap trial,
  we randomly chose 24 solutes with replacement and calculated the average
  active solute-monomer hydrogen bonds per frame.

@@

  % BJC: Clauset has an easily understood test for exponential versus power law. Would take
  % me maybe half a day to implement and generate results. Not sure if necessary though since
  % I'm just going to say that I don't know what distribution it is and we are going to
  % use a percentile.
  Hydrogen bond lifetimes appear to be distributed according to a power law or an
  exponential function. A number of researchers provide evidence that supports a 
  power law distribution~\cite{starr_fast_1999,martiniano_insights_2013}. However, these
  studies were done on extremely short timescales relative to ours, outputting positions
  every time step. Voloshin et al. studied hydrogen bonding on multiple timescales and 
  observed exponential behavior on the longest timescales~\cite{voloshin_hydrogen_2009}. 
  Due to memory limitations, we could not collect data frequently enough to provide a
  sufficient answer to this question so we instead report the 95\textsuperscript{th} 
  percentile of hydrogen bond dwell times. This places emphasis on solutes with 
  long dwell times. We reported the standard error of this calculation by bootstrapping
  the distribution of dwell times.

@@

  In the 10 wt\% water system, water molecules that spend the majority of 
  their time in the distal tail region move significantly slower than those
  close to the pore center. In Figure~\ref{fig:water_msd_comparison}, we 
  constructed the MSD curves based on water molecules that spent $>$ 95\% of their
  time outside the distal tail region. If we instead restrict our calculation to
  water molecules that spend $>$ 95\% of their time in the distal tail region, 
  the MSD of distal tail water decreases 8-fold.

  % Changing pore radius does not change conclusion here.
  In the 5 wt\% water system, water molecules that spend the majority of their 
  time in the distal tail region have MSDs comparable to those of water molecules
  close to the pore center. The MSD of distal tail water molecules is 1.71 nm$^2$.
  This anomaly is likely a consequence of low density in the distal tails (see
  Figure~\ref{S-fig:total_density}) as well as structuring of water molecules via
  hydrogen bonding. Water molecules are less likely to hydrogen bond while in the
  distal tail region since they are interspersed between chains, while those in 
  the pores stay in close proximity to each other. We observed about 9 times more  % tailvpore_hbonding.py in figures folder
  hydrogen bonding between water molecules near the pore center versus those in 
  the distal tail region. While a similar observation holds for the 10 wt\% system,
  its high water content facilitates a less crowded environment where diffusion
  of water molecules dominates.

>>>>

  In addition to geometric factors which make H\textsubscript{II} membranes
  ideal for selective separations, they have the potential to further disrupt
  conventional membrane separation techniques by being selective based not
  only on solute size and charge, but on chemical functionality as well. 
  The functional LLC monomer head groups that occupy the pore region of the
  membrane can interact with solutes. Dischinger et al.~studied the 
  performance of a Q\textsubscript{I} phase LLC membrane, which has a 
  similar pore topology to the H\textsubscript{II} phase, but a more 
  tortuous geometry, and observed a range of selectivities dependent on the
  anion coordinated to the LLC monomer.~\cite{dischinger_effect_2017} Intelligent 
  design of LLC monomers 
  %MRS4: 
  %can 
  have the potential to 
  help us tailor membranes for solute-specific
  separations.

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. The separation performance of these membranes has been 
  primarily characterized with size-exclusion experiments which emphasizes 
  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
  %MRS4: might confuse readers here - talking about both size exclusion as a method to characterize the membranes, and 
  %separation BY size exclusion; maybe rephrase?
  While size-exclusion is a useful separation, it cannot reliably purify a 
  solution where the solute size is on the same order as water. Therefore, it is
  important to take advantage of material properties other than pore size. 
  Unfortunately, interactions between solutes and pore moieties have yielded
  unclear trends in experimental transport studies.~\cite{dischinger_effect_2017}
  %MRS4: expand the above.  What was discovered, and why was it unfortuate to the thesis?  
  % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?

  Molecular dynamics (MD) simulations can give us mechanistic insights with 
  atomistic resolution so that we can directly 
  %MRS4: observe is strong, maybe describe? I'm open to other options.
  % observe 
  describe
  small solute transport
  within LLC membrane nanopores and intelligently design new membranes for 
  solute-specific separations. In our previous work, we used MD simulations to 
  determine the most likely structure of the hexagonal phase formed by the monomer
  Na-GA3C11, expanding upon the most recent experimental characterization.~\cite{coscia_understanding_2018,feng_thin_2016}
  We developed techniques for equilibrating the hexagonal phase formed by neat 
  monomer as well as with varying amounts of water in the pores.

  %BJC: is a figure with all the solutes necessary? would take up a lot of space. maybe supporting. 
  %MRS4: I kind of like it here.  We can tweak the text to be a bit shorter without losing meaninig.
  In this work, we have studied the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character. We have listed the solutes studied along with the abbreviations that
  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
  Note that, in order to avoid studying charge species, we have only studied
  %BJC: citations for pKa's
  acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
  pKa of acetic acid is 4.75. Assuming that the pKa of gallic acid is similar 
  to NaGA3C11, it is possible for our sodium salted monomer to exist at the 
  same time as protonated acetic acid.  
  %MRS4: added for clarity
  In any case, we are more interested in mechanisms of interaction with specific chemical functionality more than the behavior of specific molecules.

%MRS4: probably shouldn't capitalize the names.  Maybe make the yellow a bit darker for the text.
%  % BJC: not sure if I should just leave formatting to the journal. Thought tcolorbox was neat though
%  % I can easily change these abbreviations and have them applied to all the figures. I haven't given
%  % them much thought. Just used their residue names
%  \begin{table}
%  \centering
%  \begin{tcolorbox}[%
%  	colframe=blue,
%  	title=\centering \textbf{Solute Names and Their Abbreviations},
%  	width=0.7\textwidth,
%  	box align=center,
%  	halign=center,
%  	valign=center,
%  	fontupper=\linespread{1}\selectfont]
%
%  \begin{multicols}{2}
%
%  \textbf{Name} \\
%  Acetic Acid \\
%  Acetamide \\
%  Acetone \\
%  Butanol \\
%  Dimethyl Formamide \\
%  2,3-Dimercapto-1-propanol \\
%  Dimethyl Sulfoxide \\
%  Ethyl Acetate \\ 
%  Ethanol \\
%  Ethylene Glycol \\
%  Glycerol \\
%  Methanol \\ 
%  Propylene Carbonate \\
%  Propylene Glycol \\
%  Propanol \\
%  Ribose \\
%  Mercaptoethanol \\
%  Tetrose \\
%  Tetrahydrofuran \\
%  Urea \\
%  \columnbreak
%
%  \textbf{Abbrevation} \\
%  AcOH \\  % Acetic acid
%  AcN \\  % Acetamide
%  ACE \\  % Acetone
%  BtOH \\  % Butanol
%  DMF \\  % Dimethyl Formamide
%  DMP \\  % 2,3-Dimercapto-1-propanol
%  DMSO \\  % Dimethyl sulfoxide
%  ETAC \\  % Ethyl Acetate
%  EtOH \\  % ethanol
%  EG \\  % ethylene glycol
%  GLY \\  % glycerol
%  MeOH \\  % methanol
%  PC \\ % propylene carbonate
%  PG \\  % propylene glycol
%  PrOH \\  % propanol
%  RIB \\ 
%  ME \\ % mercaptoethanol
%  TET \\
%  THF \\ 
%  URE \\
%  
%  \end{multicols}
%  
%  %MRS2: can you put molecules in the table as well? I think it would be better for reference. Some of the larger ones may have small molecules. You can potentially partially stagger them horizontally so the size can be OK? 
%  \end{tcolorbox}
%  \caption{}\label{table:abbreviations}
%  \end{table}

@@

  We first address the structure of the pores formed in the membrane.
  Previously, we have studied dry membrane systems and some systems with 
  low water content. We 
  %MRS4: we already observed it
  %will observe 
  therefore first analyze 
  how the radial density of monomer 
  components and water change within the pore based on membrane water content.

  We then present our efforts to understand how small molecules, 
  including water, partition within the pores. From a macroscopic perspective,
  %MRS4: tweak.
  %it is straightforward 
  it might make sense
  to hypothesize that the water and polar solutes spend
  their time exclusively in the tube-like hydrophilic pore region. 
  %MRS4: However,
  our
  previous work showed that there is a gradual compositional transition from
  the hydrophilic to the hydrophobic region which means that solutes may not
  necessarily stay confined to the centers of the pores or even within the 
  pore region. We then study the gradient in composition of solutes and 
  water and any resultant influence it might have on mechanistic properties.

  %MRS4:
  %For 
  In
  the remainder of the paper, we present our observations 
  and explanations of the observed transport mechanisms exhibited by water
  and solutes. Given that the pores will restrict motion of the solutes, we
  anticipate that transport will be hindered in some way.

@@

  There are also a couple of 
  %points 
  questions
  that this study 
  % is not intended to address. 
  that are beyond the scope of this study.
  First, we will not study the concentration dependence of the observed transport
  rates. Although the average MSD might change with concentration, we are 
  focused on the underlying solute-membrane interactions that lead to the 
  observed transport mechanisms which we conjecture will 
  %MRS4: Some tone tweaks below.
  %be 
  remain roughly
  the same 
  regardless of concentration. Second, we will not study the chemical potential
  of solutes in the pores, which could give us a better understanding of 
  equilibrium solute partitioning. However, this information 
  %will not greatly enhance our
  is not needed to 
  understanding of mechanistic details in various membrane regions; 
  %Both of the
  %above points will add unnecessary levels of complexity which can be left for
  %a future study. 
  this work 
  %is a simple 
  represents
  starting point for observing
  the types of interactions which occur between isolated solutes and the
  membrane.

@@

  We observed that 
  %MRS4: added
  some
  water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition. We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent. We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95\% of their time outside of the distal tail region.

@@

  To study a given solute, we added 6, equally spaced in $z$, solute molecules to the
  center of each pore of the equilibrated cross-linked configuration. Our choice of 6
  solutes per pore provided a balance of a useful amount of data for generating 
  statistics and a low degree of interaction between solutes (see 
  Section~\ref{S-section:solute_interaction} of the Supporting Information). At each
  insertion point we placed a randomly oriented solute molecule then ran a short 
  energy minimization. We allowed the solutes to equilibrate for 5 ns using Berendsen
  pressure control then collected transport data over the course of 1 $\mu$s MD simulations.
  %MRS4: Was Berendsen pressure control used for the transport as well?  Should specify?  I thought those might have been NVT? If so, should put in an acknowledgement that it's not quite right, cite my and Pascal's paper.
  \subsection{Solute Parameterization}\label{method:parameterization}

  We parameterized the interaction potential for the monomer and solutes using 
  the Generalized AMBER Force Field (GAFF)~\cite{wang_development_2004} with the
  Antechamber package \cite{wang_automatic_2006} shipped with AmberTools16~\cite{case_ambertools16_2016}.
  We use GAFF 
  as it has been used extensively 
  %since it has been parameterized 
  for use with organic molecules.
  We
  assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
  with QUACPAC from Openeye Scientific Software.

@@

  We measured the time-averaged $z$-direction mean squared displacement (MSD) of the
  centers of mass (COM) of each solute over the course of 1 $\mu$s MD simulations using 
  Equation~\ref{eqn:tamsd}:
  \begin{equation}
	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
	\label{eqn:tamsd}
  \end{equation}
  where $\tau$ is the time lag and T is the length of the trajectory~\cite{meroz_toolbox_2015}. 
  %Generally, 
  The MSD, in standard treatments, grows according to Equation~\ref{eqn:msd_form}:
  \begin{equation} 
	\langle z^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_\alpha$ is the generalized diffusion 
  coefficient. A value of $\alpha < 1$ indicates a subdiffusive process, while a value 
  of $\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
  motion respectively.
    % MRS1: time vs. ensemble MSD better in follow-up paper.
    % BJC2: I think it makes sense to mention, otherwise it looks like we don't 
    % fully understand the theory since I talk about subdiffusion in terms of 
    % alpha which is always calculated based on ensemble MSD unless we know for sure that
    % the system is ergodic (which it isn't the case for CTRW)
  In practice, $\alpha$ corresponds to the growth of the \textit{ensemble} MSD given
  by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
  \begin{equation}
	\langle z^2(t) \rangle = \langle z(t) - z(0) \rangle
	\label{eqn:ensemble_msd}
  \end{equation}
  Since the ensemble MSD is calculated with respect to a reference position, it carries
  some dependence on its starting point. The time-averaged MSD averages over all possible
  time lags of a given length, effectively eliminating any initial configuration 
  dependence and generating	an increased number of observations. For ergodic systems, 
  both types of MSDs will be equal. Since we have a small number of solutes with which to
  generate statistics and because we are not calculating values of $\alpha$ for this 
  particular study,	we will only use the time-averaged MSD.

@@

  The $z$-direction MSD of water in the 10 wt\% system is linear. Therefore, for
  the purpose of comparison, we calculated its diffusion constant by fitting a line
  to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
  is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
  by 2 (rather than 6) because we only measured 
  %MRS4: check that this change is correct. 
  %the diffusion coefficient 
  particle displacement
  in one dimension.

@@

  The Stokes-Einstein relationship expresses the diffusion coefficient of 
  a hard spherical particle as a function that is inversely related to the
  particle's radius:
  \begin{equation}
  D = \dfrac{k_bT}{6\pi\eta fr}
  \label{eqn:stokes-einstein}
  \end{equation}
  where $k_b$ and $T$ are the Boltzmann	constant and the system temperature
  respectively and $\eta$ is the system's viscosity. Here we have also 
  included the microfriction correction factor, $f$, introduced by 
  Gierer and Wirtz~\cite{gierer_molekulare_1953,chen_diffusion_1984} for when
  solute size becomes on the order of solvent size since the solute can no 
  longer be treated as a non-interacting hard sphere. $f$ is defined in terms
  of the ratio of $r_1$ and $r_2$, the radii of the solute and solvent molecules
  respectively:
  \begin{equation}
  f = \left(1.5\dfrac{r_2}{r_1} + \dfrac{1}{1 + \dfrac{r_2}{r_1}}\right)^{-1}
  %f = \left(1.5(r_2/r_1) + \dfrac{1}{1 + (r_2/r_1)}\right)^{-1}
  \label{eqn:correction_factor}
  \end{equation}
  For consistency with the presentation of our results, rather than calculate trends
  in $D$, we will apply Equation~\ref{eqn:stokes-einstein} in order to analyze 
  trends in solute MSDs, which is only valid because all trajectories are of the 
  %MRS4: a bit strange to say you are using Stokes-einstein, but only analyzing MSD's (when MSD's don't appear in that equation)? It could be clarified a bit more.
  same length.
%  However, this assumes linear behavior
%  of the MSD, which we will show is not that case. Our main usage of the 
%  Stokes-Einstein relationship is to show that solutes in our system do not 
%  behave as it predicts.
  % Possible comps question: Stokes law restricted to Re < 0.1, but we have no flow so Re ~ 0.

@@

  In order to measure the length of hops, we first needed to detect
  when they occurred. We used an off-line change point detection 
  algorithm, implemented in the python package \texttt{ruptures}
  \cite{truong_ruptures:_2018}, in order to determine at which 
  points hops occurred in the time series of each solutes' COM. We
  used the 3 dimensional COM positions of each solute, rather than
  just the $z$-direction, in order to detect lateral hops. However,
  hop lengths are reported as their displacement the $z$-direction.
  We reported the standard error in the average hop lengths by 
  bootstrapping the 
  %MRS4:
  empirical distribution of observed
  hop lengths.
  % BJC: could add more detail about which algorithm and cost function
  % penalty I used. Seems unnecessary since it is all in my code.
  %MRS4: I would put in supporting.

  We determined the frequency of hops by dividing the total number of 
  hops by the total length of the simulation. We used the average
  frequency as the $\lambda$ parameter in a Poisson distribution. We
  calculated the 95\% confidence intervals of the distribution based
  on the Poisson cumulative distribution function.

@@

  Based on the geometric criteria proposed by Luzar and Chandler 
  \cite{luzar_effect_1996}, we determined a hydrogen bond to exist if the
  distance between the donor, D, and acceptor, A, atoms is less than 
  3.5 \AA~and the angle formed by D--H$\cdot\cdot\cdot$A is less than 30\degree. Attempts
  to describe a hydrogen bond in the context of molecular simulations has
  yielded a number of definitions with no true consensus 
  \cite{prada-gracia_quest_2013} especially since the geometry of hydrogen
  bonds has some dependence on the system being studied. The definition of
  Luzar and Chandler is easily visualized for trajectories using the 
  \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
  package which allows us to directly check the validity of identified hydrogen bonds.
  In Section~\ref{S-section:hbond_sensitivity} of the Supporting Information, we
  show that our conclusions are insensitive to this definition within a 
  reasonable range
  %MRS4:added
  of distances and angles.
  We determined the average percentage of solutes which actively participated
  in a hydrogen bond interaction with monomers each frame. We only counted
  unique solute--monomer hydrogen bond interactions, meaning solutes
  that hydrogen bond more than once simultaneously were classified as a
  single pairing event. We determined the standard error of this calculation
  by bootstrapping over each solute's trajectory. For each bootstrap trial,
  we randomly chose 24 solutes with replacement and calculated the average
  active solute-monomer hydrogen bonds per frame.

@@

  % BJC: Clauset has an easily understood test for exponential versus power law. Would take
  % me maybe half a day to implement and generate results. Not sure if necessary though since
  % I'm just going to say that I don't know what distribution it is and we are going to
  % use a percentile.
  % MRS4: maybe while we are waiting for review.
  Hydrogen bond lifetimes appear to be distributed according to a power law or an
  exponential function. A number of researchers provide evidence that supports a 
  power law distribution~\cite{starr_fast_1999,martiniano_insights_2013}. However, these
  studies were done on extremely short timescales relative to ours, outputting positions
  every time step. Voloshin et al. studied hydrogen bonding on multiple timescales and 
  observed exponential behavior on the longest timescales~\cite{voloshin_hydrogen_2009}. 
  Due to memory limitations, we could not collect data frequently enough to provide a
  %MRS4: tweaking to 
  sufficient answer to this question so when comparing solutes, we use the 95\textsuperscript{th} 
  percentile of hydrogen bond dwell times. This places emphasis on solutes with 
  long dwell times. We reported the standard error of this calculation by bootstrapping
  the distribution of dwell times.

@@

  In the 10 wt\% water system, water molecules that spend the majority of 
  their time in the distal tail region move significantly slower than those
  close to the pore center. In Figure~\ref{fig:water_msd_comparison}, we 
  constructed the MSD curves based on water molecules that spent $>$ 95\% of their
  time outside the distal tail region. If we instead restrict our calculation to
  water molecules that spend $>$ 95\% of their time in the distal tail region, 
  the MSD of distal tail water decreases 8-fold. 
  %MRS4: did it really decrease? From what?  What was the previous definision.
